Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2024-01-12 main.tex
fixing some minor errors introduced by previous commit

\begin{figure}
  \centering
  \includegraphics[height= 12cm ]{figure_1_new.png}
  \caption{\label{Fig:methods} Illustration of $K$-fold cross-validation methods for Cox regression when $k = 1$}
\end{figure}

@@

The sum of squared cross-validated deviance residuals, $\sum_{i}\hat{d}_{i}^2$, are then used as the cross-validated error, analogous to using the residual sum of squares in linear regression. We refer to this method as the \emph{cross-validated deviance residuals} approach.

>>>>

\begin{figure}
  \centering
  \includegraphics[height= 12cm ]{figure_1_HD.png}
  \caption{\label{Fig:methods} Illustration of $K$-fold cross-validation methods for Cox regression when $k = 1$}
\end{figure}

@@

The sum of squared cross-validated deviance residuals, $\sum_{i} (d^{\text{cv}}_{i})^2$, are then used as the cross-validated error, analogous to using the residual sum of squares in linear regression. We refer to this method as the \emph{cross-validated deviance residuals} approach.
